Manuscript title here

### 2024-10-05 project-plan.Rmd
la till i main
glömde ändra i gammal stycke
tog bort en "problem" som jag glömde ta bort.

@@

The outcome was defined as the presence of at least one OFI, determined by the multidisciplinary M&M conference in the “problem” registry. An OFI can be various types of errors, which are categorized into: clinical judgement error, inadequate resources, delay in treatment, missed injury, inadequate protocols, preventable death and other errors.

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate(HR), systolic blood pressure(SBP), respiratory rate(RR) and mental status. Based on these four measurements, the patients will be classified into four groups roughly based on the same value as in the ATLS trauma shock classifications.

>>>>

(Infoga bild på ATLS tenth edition)

@@

The outcome was defined as the presence of at least one OFI, determined by the multidisciplinary M&M conference in the trauma care quality registry. An OFI can be various types of errors, which are categorized into: clinical judgement error, inadequate resources, delay in treatment, missed injury, inadequate protocols, preventable death and other errors.

To classify the patients the following measurement will be used as independent variables for classification of shock regardless of their cause. Heart rate(HR), systolic blood pressure(SBP) and respiratory rate(RR). Based on these four measurements, the patients will be classified into four groups roughly based on the same value as in the ATLS trauma shock classifications.
